Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-30 content/contribution/CoDeR.tex

	% Minimal Algebra
	\begin{nestedsection}{Minimal Algebra}{model: algebra}
		The minimal algebra of CoDeR is based on that of Positive Datalog, that being ${\{\bot, \text{:-}, \wedge\}}$.
		Of these, implication $\text{:-}$ and conjunction $\wedge$ may be expressed as stream-to-stream operators, the former being extended to apply to instances as $\text{:-}_{head}$ and the latter being the window-join $\Join$ \citep{niagaraCQ}, in order to support forward-chaining processing of fixed rules;
		$\bot$ is not an operator, but the special class of values that should not exist, represented in CoDeR by the ${rif\text{:}error()}$ class from RIF \citep{w3crif}).
		% Further, in order to support both fixed-plan pattern-matching algorithms such as the Rete algorithm \citep{forgy79} and adaptive algorithms such as the Eddies algorithm \citep{eddies} and its derivatives \citep{CACQ,TCQ}, CoDeR replaces the window-join operator with the State Module of Eddies, algebraically represented by ${{}_b\Join_p}$.
		Further, in order to support both fixed-plan pattern-matching algorithms such as the Rete algorithm \citep{forgy79} and adaptive algorithms such as the Eddies algorithm \citep{eddies} and its derivatives \citep{CACQ,TCQ}, CoDeR replaces the window-join operator with the State Module of Eddies, algebraically represented by $\rstreamjoin$.
		% In addition to $\text{:-}_{head}$ and ${{}_b\Join_p}$, CoDeR utilises a pair of stream-filter operators, $\sigma_{triple}$ and $\sigma_{external}$, for identifying \emph{basic patterns} as defined in SPARQL \citep{w3csparql} and expressing the datatype functions of RIF-Core \citep{w3crifcore}, respectively.
		In addition to $\text{:-}_{head}$ and $\rstreamjoin$, CoDeR utilises a pair of stream-filter operators, $\sigma_{triple}$ and $\sigma_{external}$, for identifying \emph{basic patterns} as defined in SPARQL \citep{w3csparql} and expressing the datatype functions of RIF-Core \citep{w3crifcore}, respectively.
		Finally, as basic patterns match individual triples, the CoDeR algebra includes a graph-to-triples operator ${{}_g\pi_t}$ to translate streams $S$ from the streams of graphs recommended by the RSP community to the streams of triples on which $\sigma_{triple}$ operate.
		% In summary, the minimal algebra of CoDeR consists of the set of operators ${\{\text{:-}_{head}, {}_b{\Join_p}, \sigma_{triple}, \sigma_{external}, {}_g{\pi_t}\}}$.
		In summary, the minimal algebra of CoDeR consists of the set of operators ${\{\text{:-}_{head}, \rstreamjoin, \sigma_{triple}, \sigma_{external}, {}_g{\pi_t}\}}$.

@@

@@

					\includegraphics[width=0.45\textwidth]{basic-pattern-match}

@@

					\includegraphics[width=0.45\textwidth]{datatype-function}

@@

					\includegraphics[width=0.45\textwidth]{graph-to-triple}

@@

					\includegraphics[width=0.45\textwidth]{instance-implication}

>>>>

	% Minimal Algebra
	\begin{nestedsection}{Minimal Algebra}{model: algebra}
		The minimal algebra of CoDeR is based on that of Positive Datalog, that being ${\{\bot, \text{:-}, \wedge\}}$.
		Of these, implication $\text{:-}$ and conjunction $\wedge$ may be expressed as stream-to-stream operators, the former being extended to apply to instances as $\text{:-}_{head}$ and the latter being the window-join $\Join$ \citep{niagaraCQ}, in order to support forward-chaining processing of fixed rules;
		$\bot$ is not an operator, but the special class of values that should not exist, represented in CoDeR by the ${rif\text{:}error()}$ class from RIF \citep{w3crif}.
		% Further, in order to support both fixed-plan pattern-matching algorithms such as the Rete algorithm \citep{forgy79} and adaptive algorithms such as the Eddies algorithm \citep{eddies} and its derivatives \citep{CACQ,TCQ}, CoDeR replaces the window-join operator with the State Module of Eddies, algebraically represented by ${{}_b\Join_p}$.
		Further, in order to support both fixed-plan pattern-matching algorithms such as the Rete algorithm \citep{forgy79} and adaptive algorithms such as the Eddies algorithm \citep{eddies} and its derivatives \citep{CACQ,TCQ}, CoDeR replaces the window-join operator with the State Module of Eddies, algebraically represented by $\rstreamjoin$.
		% In addition to $\text{:-}_{head}$ and ${{}_b\Join_p}$, CoDeR utilises a pair of stream-filter operators, $\sigma_{triple}$ and $\sigma_{external}$, for identifying \emph{basic patterns} as defined in SPARQL \citep{w3csparql} and expressing the datatype functions of RIF-Core \citep{w3crifcore}, respectively.
		In addition to $\text{:-}_{head}$ and $\rstreamjoin$, CoDeR utilises a pair of stream-filter operators, $\sigma_{triple}$ and $\sigma_{external}$, for identifying \emph{basic patterns} as defined in SPARQL \citep{w3csparql} and expressing the datatype functions of RIF-Core \citep{w3crifcore}, respectively.
		Finally, as basic patterns match individual triples, the CoDeR algebra includes a graph-to-triples operator ${{}_g\pi_t}$ to translate streams $S$ from the streams of graphs recommended by the RSP community\footnote{\url{https://github.com/streamreasoning/RSP-QL/blob/master/Semantics.md}} to the streams of triples on which $\sigma_{triple}$ operates.
		% In summary, the minimal algebra of CoDeR consists of the set of operators ${\{\text{:-}_{head}, {}_b{\Join_p}, \sigma_{triple}, \sigma_{external}, {}_g{\pi_t}\}}$.
		In summary, the minimal algebra of CoDeR consists of the set of operators ${\{\text{:-}_{head}, \rstreamjoin, \sigma_{triple}, \sigma_{external}, {}_g{\pi_t}\}}$.

@@

					\includegraphics[width=0.3\textwidth]{basic-pattern-match}

@@

@@

					\includegraphics[width=0.3\textwidth]{datatype-function}

@@

					\includegraphics[width=0.3\textwidth]{graph-to-triple}

@@

					\includegraphics[width=0.3\textwidth]{instance-implication}
